---
title: "Collab.Rmd"
author: "Shan and Kris"
date: "12/1/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm ready for the weekend!!!!

yes, me too- im ready for some retail therapy tomorrow and then the holiday party. are you wearing a dress?
testing

Yes, dress, heals once a year!

oh nice! i have to decide which heels to wear... the really painful ones that are super cute or the less cute ones that dont hurt as much... or vans

## This is how much our feet will hurt based on heel-height
```{r}
library(tidyverse)
shoes <-c(1:10)
sh <- shoes/2.5
pain <- c(1:10)
x <- data.frame(sh, pain)

hurts <- ggplot(x, aes(x=sh, y=pain)) + geom_point() +  
  labs(title= "CRAP MY FEET HURT",
       x= "Heel Height",
       y= "Pain Level")
hurts
```


## NYC Flight exploration
```{r}
library(tidyverse)
library(nycflights13) #please install.packages("nycflights13")

flights

##Jan 1 data
flights %>% 
  filter(month == 1,
         day == 1)
```

##try plotly looks super fun and html widgets
